\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{charter}
\usepackage{ragged2e}

\setlength{\footskip}{4.08003pt}
\hypersetup{
  pdftitle={Resume - Kiril Kvas},    
  pdfauthor={Kiril Kvas},            
  pdfsubject={Curriculum Vitae},     
  pdfcreator={LaTeX with hyperref}, 
  pdfproducer={pdfTeX},           
  pdfkeywords={Node, Nest Typescript, AWS, Docker, Git}, 
  colorlinks=false,       
  linkcolor=magenta,                
  filecolor=magenta,          
  urlcolor=magenta                 
}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{magenta}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{5pt}  % Adjust the space here
}
%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kiril Kvas} \\ \vspace{1pt}
    \small +380981713584 $|$ \href{mailto:kirilkvas07@gmail.com}{\underline{kirilkvas07@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/kiril-kvas-999154239/}{\underline{LinkedIn}} $|$
    \href{https://github.com/rillsvai}{\underline{GitHub}}
\end{center}

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Node.js Backend Developer}{Jun 2024 -- Present}
      {mindSoft}{}
      \resumeItemListStart
        \resumeItem{Designed and configured CI/CD pipelines for microservices using Jenkins, streamlining the deployment process.}
        \resumeItem{Implemented and maintained monitoring and metrics tools such as Grafana and Prometheus, enabling immediate response to downtime and facilitating in-depth system analysis.}
        \resumeItem{Managed and actively developed Nest.js/Express-based microservices communicating via AMQP (RabbitMQ), enhancing inter-service communication and system modularity.}
        \resumeItem{Deployed microservices on AWS EC2 instances using containerization, improving scalability and resource utilization.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Node.js Backend Developer}{Feb 2023 -- Apr 2024}
      {Insiders}{}
      \resumeItemListStart
            \resumeItem{Migrated backend system from AWS EC2 to AWS Elastic Beanstalk with Docker containerization using Elastic Container Registry, resulting in a more automated and scalable ecosystem.}
            \resumeItem{Built CI/CD pipelines using GitHub Actions and AWS Amplify to automate the deployment of frontend components on AWS, improving deployment efficiency.}
            \resumeItem{Expanded and optimized Express API functionality by monitoring workload with AWS CloudWatch, significantly reducing server load.}
            \resumeItem{Developed a backend for a booking widget including payment processing using Stripe and integration with Google Calendar, enabling the customer to replace third-party services.}
            \resumeItem{Contributed to the development of a payroll system using NestJS with GraphQL and Apollo Server, enhancing system capabilities and performance.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript/TypeScript, GraphQL, Rust, C\#, SQL} \\
     \textbf{Frameworks}{: NestJS, Express, Fastify, Actix-Web, Axum, ASP.NET} \\
     \textbf{Technologies}{: Node.js, Git, RabbitMQ, GCP, Docker, GitHub Actions, AWS, Azure, Linux, PostgreSQL, MySQL, Redis, MongoDB, Apollo Server} \\
    }}
 \end{itemize}
 
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ivan Franko National University of Lviv}{}
      {Bachelor of Applied Mathematics} {Sep 2021 -- Jun 2025}
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Undergraduate Thesis} $|$ \emph{Efficiency of Classical Cryptography Algorithms Based on Elliptic Curves}}{}
          \resumeItemListStart
            \resumeItem{Conducted an in-depth study on the efficiency of classical cryptography algorithms based on elliptic curves.}
            \resumeItem{Implemented ElGamal algorithm and its elliptic curve variant, performing comprehensive analysis on their performance and security.}
            \resumeItem{Enhanced understanding of cryptography and cryptanalysis, particularly in the context of elliptic curve cryptography.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubheading
      {English}{}
      {Upper Intermediate (B2)} {}
    \resumeSubheading
      {Ukrainian}{}
      {Native} {}
  \resumeSubHeadingListEnd
  
\end{document}
